\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
Flow instabilities may be caused from pressure differences along the interface of two fluids, stresses acting in different directions, mobility differences that may exceed critical limits and heterogeneities of the domain. For example, during water flooding displacement, efficiency is related with capillary number. The higher the capillary number the higher the recovery of hydrocarbons. When the driving force of the injected fluid overcomes the capillary force, a hydrodynamic instability will occur that will cause the collapse of the interface between fluids and start forming fingers.

\medskip
Fingering problems can become more intense from the heterogeneities (i.e. natural fractures, different permeability characteristics in different zones) of the porous medium therefore, sweep efficiency may reduce further or early breakthrough may result \citep{riaz_2004, tavassoli_2015}. During immiscible $CO_{2}$ flooding, $CO_{2}$ turns into supercritical phase under under high pressure and temperature. The density of supercritical $CO_{2}$ is usually lower than the \textit{in-situ} hydrocarbons therefore it may override oil. The viscocity of supercritical $CO_{2}$ is much smaller than that of the oil thus viscous fingering and/or channeling may result. The outcome of the above operations \textit{viscous fingering}.

>>>>

\medskip
Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain. \red{For example, during water flooding, efficiency is related with capillary number. The higher the capillary number the higher the recovery of hydrocarbons (LINK THESE SENTENCES ! HOW THIS NEW SENTENCE IS RELATED TO THE PREVIOUS -- 'Flow instabilities ... of the domain' ... AND HOW IS IT RELATED WITH THE FOLLOWING SENTENCES?)}. When the driving force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.

\medskip
Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore, sweep efficiency may reduce further or early breakthrough may result \citep{riaz_2004, tavassoli_2015}. During immiscible $CO_{2}$ flooding, $CO_{2}$ turns into supercritical phase under under high pressure and temperature. The density of supercritical $CO_{2}$ is usually lower than the \textit{in-situ} hydrocarbons therefore it may override oil. The viscocity of supercritical $CO_{2}$ is much smaller than that of the oil thus viscous fingering and/or channeling may result. The outcome of the above operations \textit{viscous fingering}.
